---
title: "Analysis"
author: "Daniel Stelzer"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import some libraries:

```{r}
library(tidyverse)
library(knitr)
library(kableExtra)
library(ez)
```

Define some functions:

```{r}
show <- function(.data) {
  kable(.data, format="html", booktabs=TRUE, digits=4, escape=F, row.names=FALSE) %>% kable_styling()
}

`%notin%` <- negate(`%in%`)
```

## Import the data

The data is stored in `data_for_r.csv`, which was generated by `experiment_analyze.py` based on the various files in `tagged/`.

```{r}
raw <- read.csv("data_for_r.csv",
                header=TRUE,
                sep=",",
                stringsAsFactors=TRUE)
head(raw)
```

```{r}
str(raw)
```

"Subject" is the three-character subject code: AX1 indicates that they used experimental lists 1 and 2 ("A"; "B" uses 2 and 3, "C" uses 3 and 1), used the Zeichenlexikon last ("X"; "Y" means the Zeichenlexikon came first), and were the first subject for this combination of factors ("1").

Exceptions: PA1 indicates that they were part of the pilot experiment which always put the Zeichenlexikon last ("P"), used lists 1 and 2 ("A"; "B" uses 2 and 1), and were the first subject for this combination of factors ("1"). "E" in a subject code stands for the experimenters themselves.

"Accurate" is whether or not their identification was correct, and "time" is how many seconds it took them to make that identification.

"System" is "H" for Hantatallas (the code-based system), "S" for Sanhatallas (the drawing-based system), and "Z" for the Zeichenlexikon.

"Task" is the sign they were trying to identify, and "difficulty" is the first character of that field: 0 means no damage at all, 1 some strokes are obscured but all are present, 2 missing strokes, 3 missing components, and 4 mostly obliterated.

"Enrolled" is 1 if currently enrolled in a Hittite class and 0 if not; "semesters" is how many semesters of Hittite classes they've taken, including the current one.

Which list was used, and the order in which students tried the signs, is not included here. Modify `experiment_analyze.py` if you need those.

## Remove outlier data points

If someone took 10 seconds or less on a task, they probably knew it from memory, which isn't really testing their use of the system. Similarly, if they took 10 minutes or longer, they probably got distracted, which is similarly not testing their use of the system.

```{r}
sane <- raw %>% filter(time > 10 & time < 600)
str(sane)
```

## Remove outlier subjects

If a subject has an overall accuracy of 50% or less on any particular system, that suggests they weren't paying much attention to the task. That means we should remove them.

We also need to remove subject PBE, who is the creator of Hantatallas and thus ended up with an accuracy of 100% on that system. We're interested in how *other* people use the system, not its creator who designed the experiment. For symmetry, we may also remove PAE (the other experimenter), once we have enough other data; however, he was not involved in the development of Hantatallas or the selection of tasks.

```{r}
raw_accs <- sane %>% group_by(subject, system) %>% summarize(accuracy=mean(accurate))
raw_accs %>% show()
```

Which of these is not greater than 50%?

```{r}
accs_to_remove <- raw_accs %>% filter(accuracy <= 0.5 | accuracy >= 1.0)
show(accs_to_remove)
```

So we're going to exclude AY1, BX1, PA2, and PBE.

```{r}
removed_subjects <- unique(accs_to_remove$subject)
removed_subjects
```

```{r}
filtered <- sane %>% filter(subject %notin% removed_subjects)
str(filtered)
```

## Divide subjects into Z-H and Z-S categories

```{r}
tmp_used_h <- filtered %>% filter(system=="H")
subjs_used_h <- unique(tmp_used_h$subject)
subjs_used_h
```

```{r}
tmp_used_s <- filtered %>% filter(system=="S")
subjs_used_s <- unique(tmp_used_s$subject)
subjs_used_s
```

## Analyze accuracy

Let's get an overview of the overall accuracy, including outlier subjects.

```{r}
set.seed(1)

ggplot(data=raw_accs) +
    aes(x=accuracy, y=system, color=system, shape=system) +
    geom_jitter(width=0.01, height=0.25) +
    labs(title='Raw accuracy, including outlier subjects')
```

```{r}
ggsave('r_raw_accuracy.pdf')
```

For everything else, we're going to use the `filtered` dataset that excludes the outlier subjects. Including "enrolled" and "semesters" in the grouping, since they don't vary by subject or system, ensures that they end up in the summary afterward.

```{r}
accuracy <- filtered %>% group_by(subject, system, enrolled, semesters) %>% summarize(accuracy = mean(accurate))
show(accuracy)
```

Now we have our subject variable, one within-subjects variable (system), two between-subjects variables (enrolled and semesters), and our output variable (accuracy). But is an ANOVA really the right thing to use here?

```{r}
accs_h <- accuracy %>% filter(subject %in% subjs_used_h)
accs_s <- accuracy %>% filter(subject %in% subjs_used_s)
# ezDesign(accs_h, x=.(subject), y=.(system))
```

```{r}
ggplot(data=pivot_wider(accs_h, names_from=system, values_from=accuracy)) +
    geom_point(mapping=aes(x=Z, y=H, colour=as.factor(semesters), shape=as.factor(enrolled))) +
    geom_abline(slope=1, intercept=0)
```

```{r}
ggplot(data=pivot_wider(accs_s, names_from=system, values_from=accuracy)) +
    geom_point(mapping=aes(x=Z, y=S, colour=as.factor(semesters), shape=as.factor(enrolled))) +
    geom_abline(slope=1, intercept=0)
```

```{r}
set.seed(2)

ggplot() +
    geom_jitter(data=pivot_wider(accs_h, names_from=system, values_from=accuracy),
               mapping=aes(x=Z, y=H, shape='Hantatallas', color='Hantatallas'),
               width=0.005, height=0.005) +
    geom_jitter(data=pivot_wider(accs_s, names_from=system, values_from=accuracy),
               mapping=aes(x=Z, y=S, shape='Sanhatallas', color='Sanhatallas'),
               width=0.005, height=0.005) +
    geom_abline(slope=1, intercept=0) +
    xlim(0.5, 1.0) +
    ylim(0.5, 1.0) +
    labs(shape='System', color='System', title='Accuracy by subject and system')
```

```{r}
ggsave('r_accuracy_compare.pdf')
```

```{r}
time_anova <- ezANOVA(accs_h, dv=accuracy, wid=subject, within=system, between=.(enrolled,semesters), observed=.(enrolled,semesters), return_aov=TRUE)
time_anova
```

## Analyze time
