---
title: "Analysis"
author: "Daniel Stelzer"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import some libraries:

```{r}
library(tidyverse)
library(knitr)
library(kableExtra)
library(lme4)
library(lmerTest)
```

Define some functions:

```{r}
show <- function(.data) {
  kable(.data, format="html", booktabs=TRUE, digits=4, escape=F, row.names=FALSE) %>% kable_styling()
}

`%notin%` <- negate(`%in%`)
```

## Import the data

The data is stored in `data_for_r.csv`, which was generated by `experiment_analyze.py` based on the various files in `tagged/`.

```{r}
raw <- read.csv("data_for_r.csv",
                header=TRUE,
                sep=",",
                stringsAsFactors=TRUE)
head(raw)
```

```{r}
str(raw)
```

"Subject" is the three-character subject code: AX1 indicates that they used experimental lists 1 and 2 ("A"; "B" uses 2 and 3, "C" uses 3 and 1), used the Zeichenlexikon last ("X"; "Y" means the Zeichenlexikon came first), and were the first subject for this combination of factors ("1").

Exceptions: PA1 indicates that they were part of the pilot experiment which always put the Zeichenlexikon last ("P"), used lists 1 and 2 ("A"; "B" uses 2 and 1), and were the first subject for this combination of factors ("1"). "E" in a subject code stands for the experimenters themselves.

"Accurate" is whether or not their identification was correct, and "time" is how many seconds it took them to make that identification.

"System" is "H" for Hantatallas (the code-based system), "S" for Sanhatallas (the drawing-based system), and "Z" for the Zeichenlexikon.

"Task" is the sign they were trying to identify, and "difficulty" is the first character of that field: 0 means no damage at all, 1 some strokes are obscured but all are present, 2 missing strokes, 3 missing components, and 4 mostly obliterated.

"Enrolled" is 1 if currently enrolled in a Hittite class and 0 if not; "semesters" is how many semesters of Hittite classes they've taken, including the current one.

Which list was used, and the order in which students tried the signs, is not included here. Modify `experiment_analyze.py` if you need those.

## Remove outlier data points

If someone took 10 seconds or less on a task, they probably knew it from memory, which isn't really testing their use of the system. Similarly, if they took 10 minutes or longer, they probably got distracted, which is similarly not testing their use of the system.

```{r}
sane <- raw %>% filter(time > 10 & time < 600)
str(sane)
```

## Remove outlier subjects

If a subject has an overall accuracy of 50% or less on any particular system, that suggests they weren't paying much attention to the task. That means we should remove them.

We also need to remove subject PBE, who is the creator of Hantatallas and thus ended up with an accuracy of 100% on that system. We're interested in how *other* people use the system, not its creator who designed the experiment. For symmetry, we may also remove PAE (the other experimenter), once we have enough other data; however, he was not involved in the development of Hantatallas or the selection of tasks.

```{r}
raw_accs <- sane %>% group_by(subject, system) %>% summarize(accuracy=mean(accurate))
raw_accs %>% show()
```

Which of these is not greater than 50%?

```{r}
accs_to_remove <- raw_accs %>% filter(accuracy <= 0.5 | accuracy >= 1.0)
show(accs_to_remove)
```

So we're going to exclude AY1, BX1, PA2, and PBE.

```{r}
removed_subjects <- unique(accs_to_remove$subject)
removed_subjects
```

```{r}
filtered <- sane %>% filter(subject %notin% removed_subjects)
str(filtered)
```

## Divide subjects into Z-H and Z-S categories

```{r}
tmp_used_h <- filtered %>% filter(system=="H")
subjs_used_h <- unique(tmp_used_h$subject)
subjs_used_h
```

```{r}
tmp_used_s <- filtered %>% filter(system=="S")
subjs_used_s <- unique(tmp_used_s$subject)
subjs_used_s
```

## Analyze accuracy

Let's get an overview of the overall accuracy, including outlier subjects.

```{r}
set.seed(1)

ggplot(data=raw_accs) +
    aes(x=accuracy, y=system, color=system, shape=system) +
    geom_jitter(width=0.01, height=0.25) +
    labs(title='Raw accuracy, including outlier subjects', x='Accuracy', y='System', shape=NULL, color=NULL)
```

```{r}
ggsave('r_raw_accuracy.pdf', width=6, height=4, units="in")
```

For everything else, we're going to use the `filtered` dataset that excludes the outlier subjects. Including "enrolled" and "semesters" in the grouping, since they don't vary by subject or system, ensures that they end up in the summary afterward.

```{r}
accuracy <- filtered %>% group_by(subject, system, enrolled, semesters) %>% summarize(accuracy = mean(accurate))
show(accuracy)
```

Now we have our subject variable, one within-subjects variable (system), two between-subjects variables (enrolled and semesters), and our output variable (accuracy). But is an ANOVA really the right thing to use here?

```{r}
accs_h <- accuracy %>% filter(subject %in% subjs_used_h)
accs_s <- accuracy %>% filter(subject %in% subjs_used_s)
```

```{r}
ggplot(data=pivot_wider(accs_h, names_from=system, values_from=accuracy)) +
    geom_point(mapping=aes(x=Z, y=H, colour=as.factor(semesters), shape=as.factor(enrolled))) +
    geom_abline(slope=1, intercept=0)
```

```{r}
ggplot(data=pivot_wider(accs_s, names_from=system, values_from=accuracy)) +
    geom_point(mapping=aes(x=Z, y=S, colour=as.factor(semesters), shape=as.factor(enrolled))) +
    geom_abline(slope=1, intercept=0)
```

```{r}
set.seed(2)

ggplot() +
    geom_jitter(data=pivot_wider(accs_h, names_from=system, values_from=accuracy),
               mapping=aes(x=Z, y=H, shape='Hantatallas', color='Hantatallas'),
               width=0.005, height=0.005) +
    geom_jitter(data=pivot_wider(accs_s, names_from=system, values_from=accuracy),
               mapping=aes(x=Z, y=S, shape='Sanhatallas', color='Sanhatallas'),
               width=0.005, height=0.005) +
    geom_abline(slope=1, intercept=0) +
    xlim(0.5, 1.0) +
    ylim(0.5, 1.0) +
    labs(shape='System', color='System', x='Zeichenlexikon', y='Other system', title='Accuracy by subject and system')
```

```{r}
ggsave('r_accuracy_compare.pdf', width=6, height=4, units="in")
```

Since we only have one accuracy measure per treatment per student, we can use a repeated-measures t-test. We should probably check the assumptions first, though:

```{r}
accs_h_wide = pivot_wider(accs_h, names_from=system, values_from=accuracy) %>% mutate(diff=H-Z)
accs_s_wide = pivot_wider(accs_s, names_from=system, values_from=accuracy) %>% mutate(diff=S-Z)
head(accs_h_wide)
```

My favorite way to do this is with a Q-Q plot, because it means we can look at nice plots and eyeball it instead of just staring at a column of numbers.

```{r}
library(qqplotr)
ggplot(data=accs_h_wide, mapping=aes(sample=diff)) +
  stat_qq_band(alpha = 0.5, conf = 0.95, bandType = "pointwise", fill = "blue") +
  stat_qq_line(identity = TRUE) +
  stat_qq_point(col = "black") +
  labs(x = "Theoretical Quantiles", y = "Sample Quantiles", title="Hantatallas") + 
  theme_bw()
ggplot(data=accs_s_wide, mapping=aes(sample=diff)) +
  stat_qq_band(alpha = 0.5, conf = 0.95, bandType = "pointwise", fill = "green") +
  stat_qq_line(identity = TRUE) +
  stat_qq_point(col = "black") +
  labs(x = "Theoretical Quantiles", y = "Sample Quantiles", title="Sanhatallas") + 
  theme_bw()
```

But we can also do a Shapiro-Wilk test for numerical confidence.

```{r}
shapiro.test(accs_h_wide$diff)
```
```{r}
shapiro.test(accs_s_wide$diff)
```

The takeaway here, I think, is that we need more data on Sanhatallas. Six data points is just too few. But we should have more of those soon!

Now, do the test!

```{r}
t.test(x=accs_h_wide$H, y=accs_h_wide$Z, paired=TRUE)
```

```{r}
t.test(x=accs_s_wide$S, y=accs_s_wide$Z, paired=TRUE)
```

We could also try a Wilcox test here (replace t.test with wilcox.test) if our assumptions of normality were violated.

```{r}
wilcox.test(x=accs_s_wide$S, y=accs_s_wide$Z, paired=TRUE)
```

To get more details, we can use a generalized linear mixed model (GLMM). This basically does the same thing as the above, but uses _all_ the data points instead of just the average of them.

```{r}
glmm <- glmer(accurate ~ relevel(system, ref="Z") + (1|subject) + (1|task), data=filtered, family=binomial(link="logit"))
summary(glmm)
```

## Analyze time

For time, we have several different data points per system per subject, and we don't want to entirely collapse those down into a single mean. So instead of a simple t-test (or ANOVA), we do a mixed-effects linear model. (And we use lmerTest to get a p-value, even though the author of lme4 dislikes that, just because publishers are going to want one. Alas.)

The dataset we're using here is the `filtered` one, with outliers removed.

```{r}
str(filtered)
```

But it still includes inaccurate answers. We'd like to run our mixed-effects model both with inaccurate answers included, and with them excluded.

```{r}
only_accurate <- filtered %>% filter(accurate==1)
str(only_accurate)
```

First, run with inaccurate ones included...

```{r}
mixed <- lmer(time ~ relevel(system, ref="Z") + (1|subject) + (1|task), data=filtered)
summary(mixed)
```

...then excluded.

```{r}
mixed <- lmer(time ~ relevel(system, ref="Z") + (1|subject) + (1|task), data=only_accurate)
summary(mixed)
```

We see less significance here because we threw out a bunch of data, so the standard error increased. But the overall results are not substantially different.

Let's make a visualization to sanity-check these results, showing the difference in mean time by system by student.

```{r}
mean_times <- filtered %>% group_by(subject, system) %>% summarize(mean=mean(time), accuracy=mean(accurate))
head(mean_times)
```

```{r}
mean_diff_h = mean_times %>% filter(subject %in% subjs_used_h) %>% pivot_wider(names_from=system, values_from=c(mean, accuracy)) %>% mutate(diff = mean_Z - mean_H)
mean_diff_s = mean_times %>% filter(subject %in% subjs_used_s) %>% pivot_wider(names_from=system, values_from=c(mean, accuracy)) %>% mutate(diff = mean_Z - mean_S)
show(mean_diff_h)
show(mean_diff_s)
```

```{r}
set.seed(1)
ggplot() +
    geom_jitter(data=mean_diff_h,
               mapping=aes(x=diff, y='Hantatallas', shape='Hantatallas', color='Hantatallas'),
               width=0, height=0.2) +
    geom_jitter(data=mean_diff_s,
               mapping=aes(x=diff, y='Sanhatallas', shape='Sanhatallas', color='Sanhatallas'),
               width=0, height=0.2) +
    labs(x="Time", y="System", title="Difference of mean times", shape=NULL, color=NULL)
```

```{r}
ggsave("r_mean_time_diff.pdf", width=6, height=4, units="in")
```

```{r}
set.seed(1)

ggplot() +
    geom_point(data=mean_diff_h,
               mapping=aes(x=mean_Z, y=mean_H, shape='Hantatallas', color='Hantatallas')) +
    geom_point(data=mean_diff_s,
               mapping=aes(x=mean_Z, y=mean_S, shape='Sanhatallas', color='Sanhatallas')) +
    geom_abline(slope=1, intercept=0) +
    xlim(60, 215) +
    ylim(60, 215) +
    labs(x="Zeichenlexikon", y="Other system", title="Mean time per task", shape=NULL, color=NULL)
```

```{r}
ggsave("r_mean_times.pdf", width=6, height=4, units="in")
```

```{r}
ratios_h <- mean_diff_h %>% mutate(time_ratio = mean_H / mean_Z, acc_ratio = accuracy_H / accuracy_Z)
show(ratios_h)
```
```{r}
ratios_s <- mean_diff_s %>% mutate(time_ratio = mean_S / mean_Z, acc_ratio = accuracy_S / accuracy_Z)
show(ratios_s)
```

```{r}
set.seed(1)

ggplot() +
    geom_point(data=ratios_h,
               mapping=aes(x=time_ratio, y=acc_ratio, shape='Hantatallas', color='Hantatallas')) +
    geom_point(data=ratios_s,
               mapping=aes(x=time_ratio, y=acc_ratio, shape='Sanhatallas', color='Sanhatallas')) +
    labs(x="Time ratio", y="Accuracy ratio")
```

This plot is mostly useful to give us a sense of who the outliers are. The blue triangle at the bottom left is someone who spent basically no time using Sanhatallas, and had a correspondingly low accuracy; the red dots at the top right spent a lot of time using Hantatallas, but got a very high accuracy for their efforts.

Based on this, let's define a new metric...

## Efficiency

```{r}
eff_h <- mean_diff_h %>% mutate(efficiency_H = accuracy_H / mean_H,
                                efficiency_Z = accuracy_Z / mean_Z) %>%
                        mutate(eff_diff = efficiency_H - efficiency_Z)
show(eff_h)
eff_s <- mean_diff_s %>% mutate(efficiency_S = accuracy_S / mean_S,
                                efficiency_Z = accuracy_Z / mean_Z) %>%
                        mutate(eff_diff = efficiency_S - efficiency_Z)
show(eff_s)
```

"Efficiency" is defined as mean accuracy over mean time, to compensate for the outliers in the above plot. Let's see how it stacks up!

```{r}
set.seed(1)

ggplot() +
    geom_point(data=eff_h,
               mapping=aes(x=efficiency_Z, y=efficiency_H, shape='Hantatallas', color='Hantatallas')) +
    geom_point(data=eff_s,
               mapping=aes(x=efficiency_Z, y=efficiency_S, shape='Sanhatallas', color='Sanhatallas')) +
    geom_abline(slope=1, intercept=0) +
    labs(x="Zeichenlexikon", y="Other system", title="Efficiency (mean accuracy / mean time)", shape=NULL, color=NULL) +
    xlim(0.003, 0.014) +
    ylim(0.003, 0.014)
```

```{r}
ggsave("r_efficiency.pdf", width=6, height=4, units="in")
```

This efficiency seems to differ more between systems than accuracy does. Let's try a t-test on it.

```{r}
shapiro.test(eff_s$eff_diff)
t.test(x=eff_s$efficiency_S, y=eff_s$efficiency_Z, paired=TRUE)
wilcox.test(x=eff_s$efficiency_S, y=eff_s$efficiency_Z, paired=TRUE)
```

This suggests that the efficiency measure eliminates the outliers who caused a problem before, but we still need more data for a t-test to be properly meaningful.